---
title: "Children's inferences about unmentioned groups from generic statements - Study 3"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Loading in relevant libraries and packages
library(Rmisc) # for summarySE function
library(tidyverse) # for basically everything
library(here) # for loading in our data
library(geepack) # for GEE analyses in Study 1 - 3
library(lubridate) # for computing ages
library(emmeans)
library(lme4)
library(interactions) # for Johnson-Neyman plots
library(cowplot)
library(ggpubr)
```

```{r import_expt3, include=FALSE}
# Importing Study 3 data 
expt3 <- read_csv(here::here("02_experiment", "expt3", "data", "expt3_allparticipants.csv"),
                   col_types = cols(.default = "c",
                                    dot = "c",
                                    response = "d",
                                    condition = "f",
                                    group = "f",
                                    trial_order = "d",
                                    age_exact = "d",
                                    age_year = "d",
                                    age_categorical = "f",
                                    hispanic = "d"))

expt3$dot <- mdy(expt3$dot)
``` 

```{r drop_expt3, include=FALSE} 
 # dropping participants 
 # Criterion for dropping participants: 
 # No children were excluded for manipulation checks 
 # Children were excluded for not correctly responding to control trials in pragmatic task 
  source(here::here("03_analysis", "expt3", "code", "pidi3_drop_participants.R")) 
``` 

```{r get_test_trials_expt3, include=FALSE}
# Getting data from test trials into its own dataframe
# Several data frames will be made:
# expt3_test = test trials with responses trial by trial
# expt3_inference = if participants make inference trial by trial (yes to mentioned, no to un mentioned) 
# finally, child and adult only versions of both of those dfs
source(here::here("03_analysis", "expt3", "code", "pidi3_getting_data_from_test_trials.R"))
```

```{r analyses_expt3, include=FALSE}
# Several binomial GEEs looking at:
# number of trials participant extend property to each group (adults and kids)
source(here::here("03_analysis", "expt3", "code", "pidi3_binomial_gee.R"))

# number of trials participant extend property to each group (kids)
source(here::here("03_analysis", "expt3", "code", "pidi3_binomial_gee_child.R"))

# number of trials participants make expected inference (adults and kids)
source(here::here("03_analysis", "expt3", "code", "pidi3_binomial_gee_inf.R"))

# number of trials participants make expected inference (kids only)
source(here::here("03_analysis", "expt3", "code", "pidi3_binomial_gee_inf_child.R"))
```

```{r pformat, include=FALSE}
# formatter for p values 
source(here::here("03_analysis", "general", "pformat.R"))
```


**Property Extension.** Following the same analysis strategy described in Study 1, we first examined the likelihood of extending the target property (i.e., responding "yes") to other individuals as a function of the individual's group membership (from previously mentioned or unmentioned group), participant's age, and condition (whether the speaker was knowledgeable or unknowledgeable). Children and adults were more likely to extend the target property to members of the previously mentioned group ($\chi^2$(`r expt3_test_anova$Df[3]`) = `r round((expt3_test_anova$X2[3]),2)`, *p* `r pformat(expt3_test_anova[3,3])`). Critically, their tendency to do so depended on the speaker's knowledge of two groups (Group x Condition: $\chi^2$(`r expt3_test_anova$Df[5]`) = `r round((expt3_test_anova$X2[5]),2)`, *p* `r pformat(expt3_test_anova[5,3])`) and the participant's age (Age x Group: $\chi^2$(`r expt3_test_anova$Df[6]`) = `r round((expt3_test_anova$X2[6]),2)`, *p* `r pformat(expt3_test_anova[6,3])`; Age x Condition: $\chi^2$(`r expt3_test_anova$Df[4]`) = `r round((expt3_test_anova$X2[4]),2)`, *p* `r pformat(expt3_test_anova[4,3])`; Age x Group x Condition: $\chi^2$(`r expt3_test_anova$Df[7]`) = `r round((expt3_test_anova$X2[7]),2)`, *p* `r pformat(expt3_test_anova[7,3])`, see Figure 5A). Across all four age groups, children and adults were more likely to infer that target property was not true of individuals from the unmentioned group after hearing generics from a knowledgeable speaker compared to when they heard the exact same generic statement made by an unknowledgeable speaker (Group x Condition: 4s: $\chi^2$(`r expt3_test4_anova$Df[3]`) = `r round((expt3_test4_anova$X2[3]),2)`, *p* `r pformat(expt3_test4_anova[3,3])`, 5s: $\chi^2$(`r expt3_test5_anova$Df[3]`) = `r round((expt3_test5_anova$X2[3]),2)`, *p* `r pformat(expt3_test5_anova[3,3])`; 6s: $\chi^2$(`r expt3_test6_anova$Df[3]`) = `r round((expt3_test6_anova$X2[3]),2)`, *p* `r pformat(expt3_test6_anova[3,3])`; adults: $\chi^2$(`r expt3_testadult_anova$Df[3]`) = `r round((expt3_testadult_anova$X2[3]),2)`, *p* `r pformat(expt3_testadult_anova[3,3])`). 
```{r}

```

  We find the same pattern of results when looking at children's responses only (these analyses used children's exact age as continuous variable). Children inferred that the target property was true of individuals of the previously mentioned group but not true of individuals from the unmentioned group-but they did so only when the speaker was knowledgeable and the tendency to do increased with age (Age x Condition x Group: $\chi^2$(`r expt3_test_child_anova$Df[7]`) = `r round((expt3_test_child_anova$X2[7]),2)`, *p* `r pformat(expt3_test_child_anova[7,3])`). With age, children were less likely to extend the target property to members of the unmentioned group after hearing generic language from a knowledgeable speaker ($\beta$ = `r round(expt3_test_child_emtrends$age_exact.trend[2], 2)`, 95% CI [`r round(expt3_test_child_emtrends$asymp.LCL[2], 2)`, `r round(expt3_test_child_emtrends$asymp.UCL[2], 2)`])]), but not after hearing a generic from an unknowledgeable speaker ($\beta$ = `r round(expt3_test_child_emtrends$age_exact.trend[1], 2)`, 95% CI [`r round(expt3_test_child_emtrends$asymp.LCL[1], 2)`, `r round(expt3_test_child_emtrends$asymp.UCL[1], 2)`]). Critically, by `r round(as.numeric(expt3_test_jn_unmentioned_value), 1)` years of age (determined using the Johnson-Neyman technique, see Figure 5B; Johnson & Fay, 1950), children extended the target property to members of the unmentioned group less often after hearing a generic from a knowledgeable speaker than an unknowledgeable speaker. 

```{r}

```

**Property Inference.** Next, looking at the inferences that participants made for a given target property (i.e., infer that the mentioned group has the property but that the unmentioned does not), children and adults were more likely to make the expected inference when the generic was communicated by a knowledgeable speaker than an unknowledgeable speaker (Condition: $\chi^2$(`r expt3_inference_anova$Df[1]`) = `r round((expt3_inference_anova$X2[1]),2)`, *p* `r pformat(expt3_inference_anova[1,3])`, see Figure 6A). The tendency to make this kind of inference increased with age (Age: $\chi^2$(`r expt3_inference_anova$Df[2]`) = `r round((expt3_inference_anova$X2[2]),2)`, *p* `r pformat(expt3_inference_anova[2,3])`). While we did not find an interaction between age (when treated categorically) and condition with the adult data included in the model (Age x Condition: $\chi^2$(`r expt3_inference_anova$Df[3]`) = `r round((expt3_inference_anova$X2[3]),2)`, *p* `r pformat(expt3_inference_anova[3,3])`), we do see this interaction between age and condition when examining the child data alone (here, age treated continuously). By `r round(as.numeric(gsub("Higher", "", expt3_inference_child_jn$jn[[1]]$bounds[2])), 1)` years of age (determined using the Johnson-Neyman procedure, see Figure 6B; Johnson & Fay, 1950), children are more likely to infer that properties conveyed via generics are not true of unmentioned groups when the generic is made by a knowledgeable speaker-but children do not make this inference when the generic is made by an unknowledgeable speaker (Age x Condition: $\chi^2$(`r expt3_inference_child_anova$Df[3]`) = `r round((expt3_inference_child_anova$X2[3]),2)`, *p* `r pformat(expt3_inference_child_anova[3,3])`). The tendency to only make inferences about unmentioned groups from generics when conveyed by knowledgeable speakers increases with age ($\beta$ = `r round(expt3_inf_child_emtrends$age_exact.trend[2], 2)`, 95% CI [`r round(expt3_inf_child_emtrends$asymp.LCL[2], 2)`, `r round(expt3_inf_child_emtrends$asymp.UCL[2], 2)`]). 



```{r, include=FALSE}
expt3_test_summary_adult = summarySEwithin(data = expt3_test_adult,
                                           measurevar = "response",
                                           betweenvars = c("condition",
                                                           "age_categorical"),
                                           withinvars = "group")

expt3_inference_adult <- expt3_inference %>% 
  filter(age_exact >= 18)

expt3_inference_summary_adult = summarySE(data = expt3_inference_adult,
                                          measurevar = "inf",
                                          groupvars = c("condition",
                                                        "age_categorical"))
```

```{r, include=FALSE}
# Johnson-Neyman plot
expt3_jn_inference_plot <- 
  expt3_jnplot + 
  theme(legend.position = c(.8,.15)) +
  guides(linetype = FALSE) + 
  labs(x = "Age",
       y = "Simple slope of condition\npredicting expected inference") + 
  geom_segment(aes(x = (as.numeric(expt3_jn_value) + .6),
                        y = 4,
                        xend = (as.numeric(expt3_jn_value) + .1),
                        yend = 4),
                    colour = 'black',
                    size = .5,
                    arrow = arrow(length = unit(0.3, "cm")))+
  annotate("label", 
           x = (as.numeric(expt3_jn_value) + 1), 
           y = 4, 
           label = paste(round(as.numeric(expt3_jn_value), 1), "years"),
           label.padding = unit(0.55, "lines"),
           fontface = "bold") 

expt3_jn_test_plot_unmentioned <- 
  expt3_jn_unmentioned$plot + 
  labs(x = "Age",
       y = "",
       title = "Unmentioned group") + 
  theme(legend.position = "none",
        plot.title = element_text(face = "plain"),
        axis.title = element_text(size = 14)) +
  scale_y_continuous(
    limits = c(-5,2.5),
    breaks = c(-4, -2, 0, 2)) +
  guides(linetype = FALSE) + 
  geom_segment(aes(x = (as.numeric(expt3_test_jn_unmentioned_value) + .6),
                        y = 1.5,
                        xend = (as.numeric(expt3_test_jn_unmentioned_value) + .2),
                        yend = 1.5),
                    colour = 'black',
                    size = .5,
                    arrow = arrow(length = unit(0.3, "cm")))+
  annotate("label", 
           x = (as.numeric(expt3_test_jn_unmentioned_value) + 1), 
           y = 1.5, 
           label = paste(round(as.numeric(expt3_test_jn_unmentioned_value), 1), "years"),
           label.padding = unit(0.55, "lines"),
           fontface = "bold") 


expt3_jn_test_plot_mentioned <- 
  expt3_jn_mentioned$plot + 
  labs(x = "Age",
       y = "Simple slope of condition\npredicting extension of property",
       title = "Mentioned group") + 
  scale_y_continuous(
    limits = c(-5,2.5),
    breaks = c(-4, -2, 0, 2)) +
  theme(legend.position = c(.25,.15),
        plot.title = element_text(face = "plain"),
        axis.title = element_text(size = 14)) + 
  guides(linetype = FALSE)  

test3_plot <- ggdraw() +
  draw_plot(expt3_jn_test_plot_unmentioned, x = 0.5, y = 0, width = .5, height = 1) + 
  draw_plot(expt3_jn_test_plot_mentioned, x = 0, y = 0, width = .5, height = 1) 


```


```{r plot1_expt3, include=FALSE}
# Plot plotting how many trials participants extend property to new individuals of mentioned and unmentioned group 
source(here::here("03_analysis", "expt3", "code", "pidi3_plot_property_extension.R")) 
```

```{r, include=FALSE}
expt3_test_figure <- ggdraw() +
  draw_plot(expt3_plot_prop_extension, x = 0.025, y = .525, 
            width = .975, height = .475) +
  draw_plot(test3_plot, x = 0.025, y = 0, 
            width = .975, height = .475) + 
  draw_plot_label(label = c("A", "B"), size = 15,
                  x = c(0, 0), y = c(1, 0.5))
```


```{r plot2_expt3, include=FALSE}
# Plot plotting how many trials participants make expected inference (yes to mentioned and no to unmentioned) 
source(here::here("03_analysis", "expt3", "code", "pidi3_plot_inference.R")) 

```

```{r, include=FALSE}
expt3_inference_figure <- ggdraw() +
  draw_plot(expt3_plot_inference, x = 0.015, y = 00, 
              width = .57, height = 1) +
  draw_plot(expt3_jn_inference_plot, x = .585, y = 0, 
            width = .415, height = 1) +
  draw_plot_label(label = c("A", "B"), size = 15,
                  x = c(0, .615), y = c(1, 1))
```

```{r, echo=FALSE}
expt3_test_figure
```

*Figure 5.* (A) Proportion of trials that participants extended the target property to individuals of the mentioned and unmentioned groups by age and condition. Error bars and bands reflect 95% CIs. Small shapes reflect individual averages, and large shapes and lines reflect group averages. (B) Johnson-Neyman plots. Lines reflect differences in simple slopes of condition predicting participants' extension of the target property as a function of age and group membership (mentioned versus unmentioned). Rate of property extension to the mentioned group was significantly different across all observed age groups, and became significantly different at `r round(as.numeric(expt3_test_jn_unmentioned_value), 1)` years for the unmentioned group. 

```{r, echo=FALSE}
expt3_inference_figure
```

*Figure 6.* (A) Proportion of trials that participants made the expected inference (i.e., responded "yes" individual of mentioned group has target property but "no", individual of unmentioned group does not) by age and condition. Error bars and bands reflect 95% CIs. Small shapes reflect individual averages, and large shapes and lines reflect group averages. (B) Johnson-Neyman plot. Line reflects difference in slopes between knowledgeable and unknowledgeable speaker conditions across age. Slopes between the conditions become significantly different at `r round(as.numeric(expt3_jn_value), 1)` years-old.