---
title: "Children's inferences about unmentioned groups from generic statements - Study 2"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Loading in relevant libraries and packages
library(Rmisc) # for summarySE function
library(tidyverse) # for basically everything
library(here) # for loading in our data
library(geepack) # for GEE analyses in Study 1 - 3
library(lubridate) # for computing ages
library(emmeans) # for marginal means and slopes
library(lme4)
library(interactions) # for Johnson-Neyman plots
library(cowplot) # plotting
library(ggpubr) # plotting
```

```{r import_expt2, include=FALSE}
 # Importing Study 2 data 
expt2 <- read_csv(here::here("02_experiment", "expt2", "data", "expt2_allparticipants.csv"),
                   col_types = cols(.default = "c",
                                    dot = "D",
                                    response = "d",
                                    condition = "f",
                                    group = "f",
                                    trial_order = "d",
                                    age_exact = "d",
                                    age_year = "d",
                                    age_categorical = "f",
                                    hispanic = "d"))
``` 


```{r drop_expt2, include=FALSE} 
 # dropping participants 
 # Criterion for dropping participants: 
 # No children were excluded for manipulation checks 
 # Children were excluded for not correctly responding to control trials in pragmatic task 
 source(here::here("03_analysis", "expt2", "code", "pidi2_drop_participants.R")) 
``` 

```{r get_test_trials_expt2, include=FALSE}
# Getting data from test trials into its own dataframe
# Several data frames will be made:
# expt2_test = test trials with responses trial by trial
# expt2_inference = if participants make inference trial by trial (yes to mentioned, no to un mentioned) 
# finally, child and adult only versions of both of those dfs
source(here::here("03_analysis", "expt2", "code", "pidi2_getting_data_from_test_trials.R"))
```

```{r analyses_expt2, include=FALSE}
# Several binomial GEEs looking at:
# This study only has child participants
# number of trials participant extend property to each group
source(here::here("03_analysis", "expt2", "code", "pidi2_binomial_gee.R"))

# number of trials participants make expected inference
source(here::here("03_analysis", "expt2", "code", "pidi2_binomial_gee_inf.R"))
```

```{r pformat, include=FALSE}
# formatter for p values 
source(here::here("03_analysis", "general", "pformat.R"))
```

**Property Extension.** We found the same pattern of results as in Study 1: Children were more likely to extend the target property to members of the previously mentioned group than the unmentioned group (Group: $\chi^2$(`r expt2_test_anova$Df[2]`) = `r round((expt2_test_anova$X2[2]),2)`, *p* `r pformat(expt2_test_anova[2,3])`), and they did so more frequently when they heard generic language over specific statements (Group x Condition ($\chi^2$(`r expt2_test_anova$Df[3]`) = `r round((expt2_test_anova$X2[3]),2)`, *p* `r pformat(expt2_test_anova[3,3])`, see Figure 4A). 


```{r plot1_expt2, include=FALSE}
source(here::here("03_analysis", "expt2", "code", "pidi2_plot_property_extension.R")) 

expt2_plot_prop_extension
```

**Property Inference.** Next, we examined whether at the level of individual trials, children inferred that the target property was true of the mentioned group but not of the 
unmentioned group. We found that children more frequently made this inference after hearing the property conveyed via a generic versus a specific statement ($\chi^2$(`r expt2_inference_anova$Df[1]`) = `r round((expt2_inference_anova$X2[1]),2)`, *p* `r pformat(expt2_inference_anova[1,3])`, see Figure 4B), thus, replicating the main finding of Study 1. 


```{r plot2_expt2, include=FALSE}
source(here::here("03_analysis", "expt2", "code", "pidi2_plot_inference.R")) 
expt2_plot_inference
```


```{r, include=FALSE}
expt2_figure <- ggdraw() +
  draw_plot(expt2_plot_prop_extension, x = 0.015, y = 00, 
              width = .57, height = 1) +
  draw_plot(expt2_plot_inference, x = .585, y = 0, 
            width = .415, height = 1) +
  draw_plot_label(label = c("A", "B"), size = 15,
                  x = c(0, .615), y = c(1, 1))
```

```{r}
expt2_figure
```

*Figure 4.* (A) Proportion of trials that children extended the target property to individuals of the mentioned and unmentioned groups by condition. Error bars reflect 95% CIs. Small shapes reflect individual averages, and large shapes and lines reflect group averages. (B) Proportion of trials that children extended the target property to individuals of the mentioned and unmentioned groups by condition. 


